Extended Abstract

### 2021-05-20 paper/paper.tex
Rework abstract

\begin{abstract}
  Type checking a \picalc{} with linear and shared types without relying on type annotations entails inferring the types of newly created channels.
  But in the \picalc{} with linear and shared types (also with graded types) processes can partially use a channel and then send it away: in this case, the receiving process might further constraint the channel's inferred type.
  This means that there are non-local constraints without a most general unifier that we have to keep around.

  We approach this problem following Padovani \cite{Padovani15}: we provide a \emph{co-contextual typing inference} \cite{ErdwegBKKM15} algorithm that traverses processes bottom-up collecting constraints, then solve (some of) these constraints using well-known unification algorithms \cite{McBride03} to find the most general unifier, and defer those constraints that do not have one.
  We state clear soundness and completeness theorems for both these phases and a progress theorem that ensures that only constraints without a most general unifier are deferred.
  The totality of this work is being mechanised in Agda.
\end{abstract}

>>>>

\begin{abstract}
  To type check a \picalc{} process with linear and shared types without relying on type annotations we need to infer the types of the channels we create within the process.
  If we were to limit ourselves to the shared \picalc{}, we could traverse a process bottom-up and always eagerly solve typing constraints into substitutions that are then applied to the typing context.
  However in our setting, typing constraints do not always come with have a most general unifier, and thus cannot always be eagerly solved.
  We follow Padovani \cite{Padovani15} and provide a \emph{co-contextual typing inference} \cite{ErdwegBKKM15} algorithm that traverses processes bottom-up and, in addition to the typing context, collecting typing constraints too.
  We then solve those constraints with a most general solution by using well-known unification algorithms \cite{McBride03}, and defer the rest until more information becomes available.

  We state clear soundness and completeness theorems for both these phases and a progress theorem that ensures that only those constraints without a most general unifier are deferred.
  The totality of this work is being mechanised in Agda.
\end{abstract}
